\documentclass[a4paper,12pt]{article} 
\usepackage{xepersian}
\usepackage{graphics}
\settextfont{XBZar}
\setdigitfont{XBZar}
\fontsize{14}{15}\selectfont

\begin{document}
\begin{center}                                                                                                                                                                                       پروژه دانشجویی 

\end{center}


\noindent
   نام : ملیکا
 نام خانوادگی : زمان زاده  
 شماره دانشجویی : ۹۴۹۶۳۲۰۷۸ 
 دانشجوی رشته مهندسی کامپیوتر (فن آوری اطلاعات)
 درس:  روش پژوهش و   ارائه \\
 استاد  : جناب  آقای دکتر رضوی\\        از صفحه 76 تا 78 کتاب 
   \noindent

\vspace{0.1cm}
\vspace{0.1cm}
\vspace{0.1cm}
\begin{center}

CHALLENGES OF e-RESEARCH COLLABORATION

\end{center}
      

\begin{latin}


\vspace{0.1cm}
\vspace{0.1cm}
\vspace{0.1cm}
\noindent
In addition  to  its potential benefits, the Net  does create some new challenges  for col• laborative research.  For example,  one application  of the Net  is to create an environ• ment  in which  the  challenges  of distributed research groups  and  the  needs  of the community can be met. However, such a substitution of Net-based for real-life  con• texts presupposes  Internet efficacy and access (to hardware, bandwidth, a space, and a time) by all the participants. Such tools or skills are not  always found  among  active researchers even in today's modern universities and are much rarer in higher education institutions and research units in developing countries


\vspace{0.1cm}
\vspace{0.1cm}
\vspace{0.1cm}
\indent
Cyber scholar Mark Nunes  (see Nunes,  1997) provides an account of his experi•
\noindent
ences with Internet-based scholarly activities. They include collaborating on writing projects, planning  conferences, and participating in lists and MOOs. Nunes  outlines a host  of benefits  and  overviews problems  that  result  from  a  lack of commitment in cyberspace. He writes:

\indent
In addition, the lack of physical "space" has a serious impact on the commitment ofyour online  collaborators.  We all showed up this afternoon.  If four of us agreed to  meet at
1: 15  for some sort of online panel, I could almost guarantee  at least one of us would be missing. In the Postmodern Spacings project, at times real-time  discussion consisted of only two people. In fact, we never had more than half of the participants present  at any one meeting. In a  similar vein, online collaborative  projects like Postmodern Spacings make closure a  difficult goal. While  the medium  is wonderful for new openings, the looseness makes completion  quite a task.

\noindent
One could argue that because Nunes's  group used synchronous  groups  excessively,  a lack of commitment stemmed  from forcing synchronous  activity on busy people,  but that would not be the full story. Research collaboration  depends on frequent formal and informal conversation to be most effective. Most of us can only commit a certain amount of time in our lives for such interaction-too often the face-to-face one takes priority. The pure technical determinist might argue that an effective project management tool could eliminate wasted time, logistical complexity, and errors due to misunderstanding. The predilection for face-to-face  interaction amongst  almost all researchers  we know constrains effective collaboration-but it usually does not stop the collaborative process. As we gain more experience designing and completing collaborative e-research projects, and the tools continue to improve, this barrier will be reduced, though never eliminated. As in all life/space decisions, trade-offs between  convenience, cost, effectiveness, and time commitment are a component of the collaborative research process.
\begin{center}
COLLABORATION TOOLS  IN ACTION: A FAILED  EXAMPLE
\end{center}

\noindent
Most  of the examples in this book document  successful  applications  of e-research  tools and techniques. The following example illustrates that success is not an assured outcome. In this example we describe the context and the tools of a collaborative e-research project. 


\vspace{0.1cm}
\vspace{0.1cm}
\vspace{0.1cm}
\indent
This research  team was funded  for a  two-year  project  to investigate  and develop educational  applications for next-generation, high-speed  Internet networks. The researchers were located at seven Canadian universities, and their work focused on devel• oping  Net-based video  conference  applications,  creating  repositories  for  educational objects, and repurposing of educational video content  for distribution over the Net. The project administrative team was located in one of the universities, while a single  researcher or small team was located  at the other universities.\\
\vspace{0.1cm}
\vspace{0.1cm}
In early discussions, the researchers noted the need for asynchronous communica•
tion,  file, and project management  tools. They selected a free Net-based  product  (Com• munityZero)  that provided these and a variety of additional  tools (such as news features, synchronous chats, calendars, etc.) that could be used by the group. One of the principle investigators in the project set up a demonstration in which the original project applica• tion,  a few updated  notices, and an asynchronous  discussion were established as a proto• type of the community  collaboration  tool's potential. This prototype was demonstrated  at one of the few face-to-face meetings of the group, and all agreed to use the system. How• ever, many of the collaborators did not sign on to the system, nor did they respond to the application manager inviting them to do so.  Soon, those who had signed on noticed that the asynchronous  discussion had little new material and that no one was adding new con• tent to the collaborative workspace. The site failed to achieve critical mass and within six months was removed by the Web site owners.


\vspace{0.1cm}
\vspace{0.1cm}
\vspace{0.1cm}
Why did the system not prove beneficial? Despite the need for collaboration  tools, these application  tools were perceived as less valuable than more readily accessible and familiar tools.  Most  of the  administrative  staff,  who were located  at a  single site,  had access to a variety  of LAN-based  services.  Most  of the  remote participants  were less involved in the project and thus did not interact with the collaborative team software on a  daily basis. This particular  project was just one of many workplace obligations  for the remote  and distributed  group. Although  the software  had the capacity for the owner to push e-mail announcements to participants, there  was no way to automatically alert all members when new content was added. Thus, users logged on to a remote system only to find that there was nothing  new in most instances.  Such negative feedback quickly extin• guishes the desire to log on to external sites. After a few months of nonuse, many partic• ipants forget passwords and login I.D.s, making further  participation  impossible without negotiating with systems operators.

\vspace{0.1cm}
\vspace{0.1cm}

Thus,  a collaborative  system  like any new intervention must,  first,  add a relative
advantage (Rogers,  1995), second, be compatible with the current workload of all partic• ipants, and, third, require minimal effort to participate. The availability of more compat• ible  means  of  communication  (email  and  FTP   sites)  plus  the  lack of incentives  for participants to log in on a frequent  basis meant that the software did not add significant value to the project and thus was abandoned\\.
\\ APPLICATIONS OF COLLABORATIVE SOFTWARE BY e-RESEARCHERS


\noindent
As the example above demonstrates, the need for communication  and collaboration permeates  many aspects of e-research. This is  most obvious when there  is  a team of researchers, but  collaboration  is also useful for the solitary researcher  during  those components of the research  process when results, discussions, or questions  must be shared with others. 

\vspace{0.1cm}
\vspace{0.1cm}
\vspace{0.1cm}
 Net-based collaborative  software  is  relatively new, and we are just discovering ways  that e-research teams can use these powerful  tools. As noted in earlier  chapters, the e-research  process commences  with selection  and refinement of a research  prob• lem. Often this process is iterative, as various drafts are shared with sponsors, supervi• sors, or members of the research  team. Placing  initial drafts in a Net-accessible file space  allows  for  controlled access to  important documents.  During the  literature review process, a collaborative workspace is also useful for documenting, summarizing, and sharing insights from research. Each of the three software packages reviewed later in this section provides space for listing and annotating Web sites, databases, and other references found  on the Net. The polling  feature of these  collaborative  packages  is handy for conducting quick surveys of opinions  and priorities of team members. The calendar feature is useful for setting deadlines and for reminding members of real-time meetings and consultations. During  the data collection  phase of the research,  the cal• endar is also useful for scheduling interviews and for circulating and archiving drafts of survey instruments or coding  protocols. An important feature of much  qualitative research is the memoing  feature (Nunes,  1997), by which researchers document ideas, insights, questions, and observations  during  the data collection  and analysis phases of research. Bogdan and Biklen (1982) extend the role of these memos in research to "the mainstay  of qualitative research  ... a written account  of what  the  researcher hears, sees, experiences, and thinks in the course of collecting  and reflecting  on the data in a qualitative study" (p.  74).  

 \vspace{0.1cm}
\vspace{0.1cm}
\vspace{0.1cm}          
Quantitative data sets can also be shared in common  workspace  so individual members can run tests on the data without  bothering other  team members for access. Finally, in the dissemination  stage, opinions  and suggestions can be polled  and final drafts  of results and "to do" lists can be shared amongst  members. Although  they are not necessarily Web-based, Microsoft  Word's editing tools provided  convenient ways to suggests  edits  and add comments  as we composed  this book.  These tools are  also very useful when marking student papers and exercises. Considerable time can be saved when using Microsoft's editing  tools by displaying  the "reviewing" toolbar  from the "view" and "toolbars" options. The review tool bar allows one to quickly add comments and edits, accept or reject the edits of coauthors, and turn the edit feature on and off.
 \vspace{0.1cm}
\vspace{0.1cm}


There are a number of software packages on the market that are designed to sup• port these functions. The first generation  of these products creates a shared workspace on a central,  Net-connected server.  Individual  users  log  on to access and to add to these central  services. More recently,  software has been designed  to use the comput• ing power  of remote users more extensively  and  to  allow team  members to  share resources and communicate through  "peer-to-peer" technologies. The most infamous of these  peer-to-peer packages  is Napster,  which  revolutionized how  commercial music is distributed.  We  review three  of these products,  not to endorse  them,  but to illustrate  how these tools can be used to enhance  the e-research process.
 \vspace{0.1cm}
\vspace{0.1cm}


MICROSOIT'S SHAREPOINT™ TEAM SERVICES
 \vspace{0.1cm}
\vspace{0.1cm}

\noindent
SharePoint Team Services were introduced  as components  of the Microsoft Office, version  XP  and  were also included  with  later  versions  of Front   Page.  SharePoint 






\end{latin}


\end{document}


